Appendix to "Spatio-temporal estimates of HIV risk group proportions for adolescent

### 2022-06-05 src/docs_paper/appendix.Rmd
Work on the manuscript #128

# Statistical modelling of risk group proportions

@@

We index the four risk groups given in Table by $k \in \{1, 2, 3, 4\}$ and we denote being in either the third or fourth risk group by $k = 3^{+}$.
Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts.
For each district $i \in \{1, \ldots, n\}$, year $t \in \{1999, \ldots, 2018\}$, age category $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$, and risk group $k \in \{1, 2, 3^{+}\}$ we consider a multinomial random vector
\begin{equation}
    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}).
\end{equation}
The number of women in risk group $k$ is $y_{itak}$ and the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, where $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.
To efficiently model this data we used the multinomial-Poisson transformation, which allows multinomial logistic regression models to be cast as equivalent Poisson log-linear models [@baker1994multinomial; @lee2017poisson]
\begin{align}
    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \label{eq:poisson} \\
    \log(\kappa_{itak}) &= \eta_{itak}, \label{eq:linearpredictor}
\end{align}
for particular choice of the linear predictor $\eta_{itak}$, described in more detail in Section.

To estimate the proportion of those in the $k = 3^{+}$ risk group that were respectively in the $k = 3$ and $k = 4$ risk groups, we fit a separate logistic regression model of the form
\begin{align}
    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \\
    q_{ia} &= p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}, \\
    q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), 
\end{align}
for choice of the linear predictor $\eta_{ia}$, described in more detail in Section.
This approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question to estimate the proportions $\{p_{ia4}\}$.
As all such surveys occurred in 2013-2018, $q_{ia}$ was assumed to be constant over time.

To quantify uncertainty from our model, we took posterior samples $s = 1, \ldots, 1000$ from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via
\begin{align*}
    p_{ita3}^s &= (1 - q_{ia}^s)p_{ita{3^+}^s}, \\
    p_{ita4}^s &= q_{ia}^s p_{ita{3^+}}^s.
\end{align*}
As transactional sex is too inclusive to directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that the population size estimates for FSW aggregated to a national level matched those of @stevens2022estimating.
In making this adjustment, we assumed that subnational variation in the FSW proportion corresponds to that of the transactional sex proportion.
We calculated the mean, median, 2.5\% and 97.5\% quantiles for the risk group probabilities empirically using these adjusted samples.
To produce aggregated estimates, such as the age category 15-24 and national estimates, we weighted the adjusted samples by population sizes $N_{ita} = \sum_k N_{itak}$ obtained from the Naomi model [@eaton2021naomi].

@@

The multinomial-Poisson transformation reframes a given multinomial logisitic regression model as an equivalent Poisson log-linear model of the form
\begin{align}
    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \\
    \log(\kappa_{itak}) &= \eta_{itak},
\end{align}
for suitable choice of linear predictor $\eta_{itak}$.
Category probabilities are then obtained by applying the softmax function to the linear predictor as follows
\begin{equation}
    p_{itak} = \frac{\exp(\eta_{itak})}{\sum_{k = 1}^{3^{+}} \exp(\eta_{itak})} = \frac{\kappa_{itak}}{\sum_{k = 1}^{3^{+}} \kappa_{itak}}.
\end{equation}
In the equivalent model, the sample sizes $m_{ita} = \sum_k y_{itak}$ are treated as random rather than fixed as they would be in the multinomial logistic regression model.
In particular, following Equation, the sample sizes follow a Poisson distribution
\begin{equation}
    m_{ita} \sim \text{Poisson} \left( \kappa_{ita} \right),
\end{equation}
where the intensity $\kappa_{ita} = \sum_k \kappa_{itak}$ is given by a sum of intensities over each category.
The basis of the Poisson trick is that, conditional on their sum, Poisson counts are jointly multinomially distributed [@mccullagh1989generalized]
\begin{equation}
    \mathbf{y}_{ita} \, | \, m_{ita} \sim \text{Multinomial} \left( m_{ita}; \frac{\kappa_{ita1}}{\kappa_{ita}}, \ldots, \frac{\kappa_{itaK}}{\kappa_{ita}} \right).
\end{equation}
As such, the joint distribution of $p(\mathbf{y}_{ita}, m_{ita})$ is
\begin{align}
p(m_{ita}) p(\mathbf{y}_{ita} \, | \, m_{ita}) 
&= \exp(-\kappa_{ita}) \frac{(\kappa_{ita})^{m_{ita}}}{m_{ita}!} \times \frac{m_{ita}!}{\prod_k y_{itak}!} \prod_k \left( \frac{\kappa_{itak}}{\kappa_{ita}} \right)^{y_{itak}} \\
&= \prod_k \left( \frac{\exp(-\kappa_{itak}) \left( \kappa_{itak} \right)^{y_{itak}}}{y_{itak}!} \right) \\
&= \prod_k \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right). \label{eq:prodpoisson}
\end{align}
Equation corresponds to the product of $K$ independent Poisson likelihoods, and the joint distribution over all the data $\{\mathbf{y}_{ita}, m_{ita}\}_{i, t, a}$ is given by $\prod_{i, t, a, k} \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right)$.
The Poisson log-linear model, which vicariously includes the sample sizes as random, is equivalent only when these normalisation constants are recovered exactly by the model.
To ensure that this is the case, we included observation-specific random effects $\theta_{ita}$ in the equation for the linear predictor in every model we considered.
Multiplying each of $\{\kappa_{itak}\}_{k = 1}^K$ by $\exp(\theta_{ita})$ has no effect on the multinomial probabilities, but does provide the flexibility required for $\kappa_{ita}$ to exactly recover $m_{ita}$ as desired.
Although in theory an improper prior $\theta_{ita} \propto 1$ should be used, in practise, by keeping $\eta_{ita}$ small so that arbitrarily large values of the observation-specific random effects $\theta_{ita}$ are not required, it is sufficient (and practically preferable for inference) to instead use a vague prior.
As such, we set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).

@@

We considered eight models (Table~\ref{tab:multinomial-models}) for $\eta_{ita}$ of the form $\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk} + \delta_{itk}$.
Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to ensure the sample sizes $m_{ita}$ were recovered exactly, as required for the Poisson log-linear model to be equivalent to the multinomial logistic regression.
To capture age-specific proportion estimates for each category $k = 1, 2, 3^{+}$, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and age-category random effects $\alpha_{ak} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
Owing to country-level heterogeneity in the data, we also included country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects, as well as separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure.
All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$
where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.

To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the age-category, country-category, space-category and year-category random effects did not alter overall category probabilities.
For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
Together, these were\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.}:
\begin{enumerate}
    \item Category $\sum_k \beta_k = 0$
    \item Age $\sum_a \alpha_{ak} = 0, \, \forall \, k$
    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
    \item Spatio-temporal $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
\end{enumerate}

@@

The surveys we used utilise a complex design, in which each individual has an unequal probability of being included in the sample.
For example, the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling.
To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y_{itak}$ are replaced by effective counts $y^\star_{itak}$ calculated using survey weights $w_{itak}$.
We multiplied direct estimates produced using the `survey` package \citep{JSSv009i08} by the Kish effective sample size \citep{kish1965survey}
\begin{equation}
    m^\star_{itak} = \left(\sum_{itak} w_{itak} \right)^2 / \sum_{itak} {w_{itak}}^2
\end{equation}
to obtain $y^\star_{itak}$.
As these counts may not be integers, the Poisson likelihood in Equation~\eqref{eq:poisson} is inappropriate.
Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, as implemented by `family = "xPoisson"` in `R-INLA`, given by
\begin{equation}
    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right).
\end{equation}

@@

\begin{table}[htb]
\small
\centering
\begin{tabularx}{\textwidth}{llllll}
\midrule
Model ID & Intercept ($\beta_0$) & Age ($\alpha_a$) & Country ($\zeta_c$) & Spatial ($\phi_i$) & Covariates \\ 
\midrule
L1 & Constant & IID & IID & IID & None \\
L2 & Constant & IID & IID & Besag & None \\
L3 & Constant & IID & IID & IID & \texttt{cfswever} \\
L4 & Constant & IID & IID & Besag & \texttt{cfswever} \\
L5 & Constant & IID & IID & IID & \texttt{cfswrecent} \\
L6 & Constant & IID & IID & Besag & \texttt{cfswrecent} \\
\midrule
\end{tabularx}
\caption{The logistic regression models that were considered. \texttt{cfswever} denotes the proportion of men who have ever paid for sex and \texttt{cfswrecent} denotes the proportion of men who have paid for sex in the past 12 months \citep{hodgins2022population}.}
\label{tab:logistic-models}
\small
\end{table}

We considered six logistic regression models (Table~\ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_c \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
We considered two specifications (IID, Besag) for the spatial random effects $\phi_i$.
To aid estimation with sparse data, we also considered national-level covariates for the proportion of men who have paid for sex ever \texttt{cfswever} or in the last twelve months \texttt{cfswrecent}, available from \citet{hodgins2022population}.
For both random effect precision parameters $\tau \in \{\tau_\alpha, \tau_\zeta\}$ as before we use the PC prior with base model $\sigma = 0$ and $\mathbb{P}(\sigma > 2.5 = 0.01)$.
For the regression parameters $\beta \in \{\beta_\texttt{cfswever}, \beta_\texttt{cfswrecent}\}$ we used the prior $\beta \sim \mathcal{N}(0, 2.5^2)$.

@@

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics{figures/fsw-logit-information-criteria.pdf}}
    \caption{Logistic regression model performance.}
    \label{fig:logistic-model-performance}
\end{figure}

@@

@@

# Supplementary figures

# Supplementary tables

>>>>

# Modelling of risk group proportions

@@

We index the four risk groups given in Table X by $k \in \{1, 2, 3, 4\}$ and denote being in either the third or fourth risk group by $k = 3^{+}$.
Let $c \in \{1, \ldots, 13\}$ denote the 13 studied AGYW priority countries, each partitioned into districts according to Table X.
For each district $i \in \{1, \ldots, n\}$, year $t \in \{1999, \ldots, 2018\}$, age category $a \in \{\text{15--19}, \text{20--24}, \text{25--29}\}$, and risk group $k \in \{1, 2, 3^{+}\}$ we consider the multinomial random vector
\begin{equation}
    \y_{ita} = (y_{ita1}, \ldots, y_{ita3^{+}})^\top \sim \text{Multinomial}(m_{ita}; \, p_{ita1}, \ldots, p_{ita3^{+}}),
\end{equation}
where the number of women in risk group $k$ is $y_{itak}$, the sample size is $m_{ita} = \sum_{k = 1}^{3^{+}} y_{itak}$, and $p_{itak} > 0$ is the probability of membership of the $k$th risk group with $\sum_{k = 1}^{3^{+}} p_{itak} = 1$.

To efficiently model this data we used the multinomial-Poisson transformation, which allows multinomial logistic regression models to be cast as equivalent Poisson log-linear models [@baker1994multinomial] of the form
\begin{align}
    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \label{eq:poisson} \\
    \log(\kappa_{itak}) &= \eta_{itak}, \label{eq:linearpredictor}
\end{align}
for suitable choice of the linear predictor $\eta_{itak}$, which we describe in more detail in Section.
Then, to estimate the proportion of those in the $k = 3^{+}$ risk group that were respectively in the $k = 3$ and $k = 4$ risk groups, we fit a separate logistic regression model of the form
\begin{align}
    y_{ia4} &\sim \text{Binomial} \left( y_{ia3} + y_{ia4}, q_{ia} \right), \\
    q_{ia} &= p_{ia4} / (p_{ia3} + p_{ia4}) = p_{ia4} / p_{ia{3^+}}, \\
    q_{ia} &= \text{logit}^{-1} \left( \eta_{ia} \right), 
\end{align}
again for suitable choice of the linear predictor $\eta_{ia}$, which we describe in more detail in Section.
This approach allowed us to include all surveys in the multinomial regression model, but only those surveys with a specific transactional sex question to estimate the proportions $\{p_{ia4}\}$.
As all such surveys occurred in 2013-2018, in the logistic regresion model $q_{ia}$ was assumed to be constant over time.

To quantify uncertainty from our model, we took 1000 posterior samples, indexed by $s$, from each of the multinomial $\{p_{itak}^s\}$ and logistic regression $\{q_{ia}^s\}$ models.
Samples $p_{ita3}^s$ and $p_{ita4}^s$ were then generated by splitting samples from the $k = 3^{+}$ category of the multinomial model via the equations
\begin{align*}
    p_{ita3}^s &= (1 - q_{ia}^s)p_{ita{3^+}^s}, \\
    p_{ita4}^s &= q_{ia}^s p_{ita{3^+}}^s.
\end{align*}
Next, as transactional sex is too inclusive to directly correspond to sex work [@wamoyi2016transactional], we adjusted our samples so that at a national level, the population size estimates match externally produced age-country specific FSW population size estimates, which we calculate in Section. 
In making this adjustment, we assumed that subnational variation in the FSW proportion corresponds to that of the transactional sex proportion.
We calculated the mean, median, 2.5\% and 97.5\% quantiles for the risk group probabilities empirically using these adjusted samples.
To produce aggregated estimates, such as the age category 15-24 and national estimates, we weighted the adjusted samples by population sizes $N_{ita} = \sum_k N_{itak}$ obtained from the Naomi model [@eaton2021naomi].

@@

The transformation reframes a given multinomial logisitic regression model as an equivalent Poisson log-linear model of the form
\begin{align}
    y_{itak} &\sim \text{Poisson}(\kappa_{itak}), \\
    \log(\kappa_{itak}) &= \eta_{itak}.
\end{align}
Category probabilities are obtained by applying the softmax function to the linear predictor as follows
\begin{equation}
    p_{itak} = \frac{\exp(\eta_{itak})}{\sum_{k = 1}^{3^{+}} \exp(\eta_{itak})} = \frac{\kappa_{itak}}{\sum_{k = 1}^{3^{+}} \kappa_{itak}}.
\end{equation}
In the equivalent model, the sample sizes $m_{ita} = \sum_k y_{itak}$ are treated as random, rather than fixed as they would be in the multinomial logistic regression model, and follow a Poisson distribution
\begin{equation}
    m_{ita} \sim \text{Poisson} \left( \kappa_{ita} \right),
\end{equation}
where the intensity $\kappa_{ita} = \sum_k \kappa_{itak}$ is given by a sum of intensities over each category.
The basis of the Poisson trick is that, conditional on their sum, Poisson counts are jointly multinomially distributed [@mccullagh1989generalized]
\begin{equation}
    \mathbf{y}_{ita} \, | \, m_{ita} \sim \text{Multinomial} \left( m_{ita}; \frac{\kappa_{ita1}}{\kappa_{ita}}, \ldots, \frac{\kappa_{itaK}}{\kappa_{ita}} \right).
\end{equation}
As such, the joint distribution of $p(\mathbf{y}_{ita}, m_{ita})$ is
\begin{align}
p(m_{ita}) p(\mathbf{y}_{ita} \, | \, m_{ita}) 
&= \exp(-\kappa_{ita}) \frac{(\kappa_{ita})^{m_{ita}}}{m_{ita}!} \times \frac{m_{ita}!}{\prod_k y_{itak}!} \prod_k \left( \frac{\kappa_{itak}}{\kappa_{ita}} \right)^{y_{itak}} \\
&= \prod_k \left( \frac{\exp(-\kappa_{itak}) \left( \kappa_{itak} \right)^{y_{itak}}}{y_{itak}!} \right) \\
&= \prod_k \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right). \label{eq:prodpoisson}
\end{align}
Equation corresponds to the product of $K$ independent Poisson likelihoods, and the joint distribution over all the data $\{\mathbf{y}_{ita}, m_{ita}\}_{i, t, a}$ is given by $\prod_{i, t, a, k} \text{Poisson} \left( y_{itak} \, | \, \kappa_{itak} \right)$.
The Poisson log-linear model, which vicariously includes the sample sizes as random, is equivalent only when these normalisation constants are recovered exactly by the model.
To ensure that this is the case, we included observation-specific random effects $\theta_{ita}$ in the equation for the linear predictor in every model we considered.
Multiplying each of $\{\kappa_{itak}\}_{k = 1}^K$ by $\exp(\theta_{ita})$ has no effect on the multinomial probabilities, but does provide the flexibility required for $\kappa_{ita}$ to exactly recover $m_{ita}$ as desired.
Although in theory an improper prior $\theta_{ita} \propto 1$ should be used, in practise, by keeping $\eta_{ita}$ small so that arbitrarily large values of the observation-specific random effects $\theta_{ita}$ are not required, it is sufficient (and practically preferable for inference) to instead use a vague prior.
As such, we set $\theta_{ita} \sim \mathcal{N}(0, \tau_\theta^{-1})$, with fixed precision $\tau_\theta = 0.000001$ (or a standard deviation of $\sigma_\theta = 1000$).

@@

\begin{table}[htb]
\small
\centering
\begin{tabularx}{\textwidth}{lllllll}
\midrule
Model ID & Category ($\beta_k$) & Age ($\alpha_{ak}$) & Country ($\zeta_{ck}$) & Spatial ($\phi_{ik}$) & Temporal ($\gamma_{tk}$) & Spatio-temporal ($\delta{itk}$) \\
\midrule
M1 & IID & IID & IID & IID & IID & \xmark \\
M1x & IID & IID & IID & IID & IID & IID $\otimes$ IID \\
M2 & IID & IID & IID & Besag & IID & \xmark \\
M2x & IID & IID & IID & Besag & IID  & Besag $\otimes$ IID \\
M3 & IID & IID & IID & IID & AR1 & \xmark \\
M3x & IID & IID & IID & IID & AR1 & IID $\otimes$ AR1 \\
M4 & IID & IID & IID & Besag & AR1 & \xmark \\
M4x & IID & IID & IID & Besag & AR1 & Besag $\otimes$ AR1 \\
\midrule
\end{tabularx}
\caption{The multinomial regression models that we considered. Observation random effects $\theta_{ita}$ are omitted from this table.}
\label{tab:multinomial-models}
\small
\end{table}

We considered eight models (Table~\ref{tab:multinomial-models}) for $\eta_{ita}$ of the form
$$
\eta_{ita} = \theta_{ita} + \beta_k + \alpha_{ak} + \zeta_{ck} + \phi_{ik} + \gamma_{tk} + \delta_{itk}.
$$
Observation random effects $\theta_{ita}$ with a diffuse prior, $\mathcal{N}(0, 1000^2)$, were included in every model to ensure the sample sizes $m_{ita}$ were recovered exactly, as required for equivalency of the models.
To capture country-specific proportion estimates for each category $k = 1, 2, 3^{+}$, we included category random effects $\beta_k \sim \mathcal{N}(0, \tau_\beta^{-1})$ and country-category random effects $\zeta_{ck} \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
We allowed heterogeneity in risk group proportions by age by including age-country-category random effects $\alpha_{ack} \sim \mathcal{N}(0, \tau_\alpha^{-1})$.
We considered two specifications, independent and identically distributed (IID) and Besag, for the space-category $\phi_{ik}$ random effects and two specifications, IID and first order autoregressive (AR1), for the year-category $\gamma_{tk}$ random effects, as well as separable space-year-category interactions $\delta_{itk}$ with corresponding Kronecker product structure.
All random effect precision parameters $\tau \in \{\tau_\beta, \tau_\alpha, \tau_\zeta, \tau_\phi, \tau_\gamma\, \tau_\delta\}$ were given independent penalised complexity (PC) priors [@simpson2017penalising] with base model $\sigma = 0$ given by $p(\tau) = 0.5 \nu \tau^{-3/2} \exp \left( - \nu \tau^{-1/2} \right)$
where $\nu = - \ln(0.01) / 2.5$ such that  $\mathbb{P}(\sigma > 2.5) = 0.01$.

To ensure interpretable posterior inferences of random effect contribution, we applied sum-to-zero constraints such that the country-category, age-country-category, space-category and year-category random effects did not alter overall category probabilities.
For the space-year-category random effects, we analogously applied sum-to-zero constraints to maintain roles of the space-category and year-category random effects.
Together, these were\footnote{The constraints for the space-year-category random effects were unable to be implemented fully, though this only effects the variance components interpretation.}:
\begin{enumerate}
    \item Category $\sum_k \beta_k = 0$
    \item Country $\sum_c \zeta_{ck} = 0, \, \forall \, k$
    \item Age-country $\sum_a \alpha_{ack} = 0, \, \forall \, k \quad \text{TODO}$,
    \item Spatial $\sum_i \phi_{ik} = 0, \, \forall \, k$
    \item Temporal $\sum_t \gamma_{tk} = 0, \, \forall \, k$
    \item Spatio-temporal $\sum_i \delta_{itk} = 0, \, \forall \, t, k;
\quad \sum_t \delta_{itk} = 0, \, \forall \, i, k;
\quad \sum_k \delta_{itk} = 0, \, \forall \, i, t$
\end{enumerate}

@@

The surveys we used utilise a complex design, in which each individual has an unequal probability of being included in the sample.
For example, the DHS often employs a two-stage cluster design, first taking an urban rural stratified sample of ennumeration areas, before selecting households from each ennumeration area using systematic sampling.
To account for the survey design, we use a weighted pseudo-likelihood where the observed counts $y_{itak}$ are replaced by effective counts $y^\star_{itak}$ calculated using survey weights $w_{itak}$.
We multiplied direct estimates produced using the `survey` package [@JSSv009i08] by the Kish effective sample size [@kish1965survey]
\begin{equation}
    m^\star_{itak} = \left(\sum_{itak} w_{itak} \right)^2 / \sum_{itak} {w_{itak}}^2
\end{equation}
to obtain $y^\star_{itak}$.
As these counts may not be integers, the Poisson likelihood in Equation~\eqref{eq:poisson} is inappropriate.
Instead, we used a generalised Poisson pseudo-likelihood $y^\star \sim \text{xPoisson}(\kappa)$, as implemented by `family = "xPoisson"` in `R-INLA`, given by
\begin{equation}
    p(y^\star) = \frac{\kappa^{y^\star}}{\left \lfloor{y^\star!}\right \rfloor } \exp \left(- \kappa \right).
\end{equation}

@@

\begin{table}[htb]
\small
\centering
\begin{tabularx}{\textwidth}{llllll}
\midrule
Model ID & Intercept ($\beta_0$) & Age ($\alpha_a$) & Country ($\zeta_c$) & Spatial ($\phi_i$) & Covariates \\ 
\midrule
L1 & Constant & IID & IID & IID & \xmark \\
L2 & Constant & IID & IID & Besag & \xmark \\
L3 & Constant & IID & IID & IID & \texttt{cfswever} \\
L4 & Constant & IID & IID & Besag & \texttt{cfswever} \\
L5 & Constant & IID & IID & IID & \texttt{cfswrecent} \\
L6 & Constant & IID & IID & Besag & \texttt{cfswrecent} \\
\midrule
\end{tabularx}
\caption{The logistic regression models that were considered. \texttt{cfswever} denotes the proportion of men who have ever paid for sex and \texttt{cfswrecent} denotes the proportion of men who have paid for sex in the past 12 months.}
\label{tab:logistic-models}
\small
\end{table}

We considered six logistic regression models (Table~\ref{tab:logistic-models}) each including a constant $\beta_0 \sim \mathcal{N}(-2, 1^2)$, age random effects $\alpha_a \sim \mathcal{N}(0, \tau_\alpha^{-1})$ and country random effects $\zeta_c \sim \mathcal{N}(0, \tau_\zeta^{-1})$.
We considered two specifications (IID, Besag) for the spatial random effects $\phi_i$.
To aid estimation with sparse data, we also considered national-level covariates for the proportion of men who have paid for sex ever \texttt{cfswever} or in the last twelve months \texttt{cfswrecent}, available from @hodgins2022population.
For both random effect precision parameters $\tau \in \{\tau_\alpha, \tau_\zeta\}$ we used the PC prior with base model $\sigma = 0$ and $\mathbb{P}(\sigma > 2.5 = 0.01)$.
For the regression parameters $\beta \in \{\beta_\texttt{cfswever}, \beta_\texttt{cfswrecent}\}$ we used the prior $\beta \sim \mathcal{N}(0, 2.5^2)$.

@@

\begin{figure}[h]
    \centering
    \makebox[\textwidth][c]{\includegraphics{depends/fsw-logit-information-criteria.pdf}}
    \caption{Logistic regression model performance.}
    \label{fig:logistic-model-performance}
\end{figure}

@@

# Age-country FSW population size estimates

We obtained estimates of adult (15-49) FSW population size from @stevens2022estimating.

@@
